data_cleaning_longer_period

### 2023-08-15 code/analysis_Redo.Rmd
tuning parameters

did2s(
      data = dfc %>% 
        select(ID, Year, Tx, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, Assets, Liabilities) %>% 
        mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, 
               Efficiency = ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
               Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
        inner_join(dfc %>% filter(Year == 2010 ) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

>>>>

did2s(
      data = dfc %>% 
        select(ID, Year, Tx, STATE, Sites, htn.rate, dm.rate, imm.rate, crc.rate, pap.rate, childbmi.rate, adultbmi.rate, ivd.rate, cad.rate, asthma.rate, Total, ngla_net_gain_loss, ngla_revenue, ngla_expense, Staff, months_of_cash, quick_ratio, fringe_rate, Assets, Liabilities) %>% 
        mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, 
               Efficiency = ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
               Altman = 6.56 * Liquidity + 3.26 * Profitability + 6.72 * Efficiency + 1.05 * NetWorth) %>% 
        inner_join(dfc %>% filter(Year == 2010 & ngla_net_gain_loss/ngla_revenue > 0.03) #& ngla_net_gain_loss/ngla_revenue < 0.03)  ngla_net_gain_loss/Assets < 0.05
                   %>% select(ID, Pct.NHA:Pct.COM) %>% unique() , by = c("ID")) , 
      yname = "Altman", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

### 2023-08-15 code/data_cleaning_longer.Rmd
tuning parameters

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

>>>>

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1 ) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))
